---
title: "Data Cleaning and Exploratory Data Analysis"
editor_options: 
  chunk_output_type: inline
---

Airbnb challenges you to predict in which country a new user will make his or her first booking

In this challenge, you are given a list of users along with their demographics, web session records, and some summary statistics. You are asked to predict which country a new user's first booking destination will be. All the users in this dataset are from the USA.

There are 12 possible outcomes of the destination country: 'US', 'FR', 'CA', 'GB', 'ES', 'IT', 'PT', 'NL','DE', 'AU', 'NDF' (no destination found), and 'other'. Please note that 'NDF' is different from 'other' because 'other' means there was a booking, but is to a country not included in the list, while 'NDF' means there wasn't a booking.

The training and test sets are split by dates. In the test set, you will predict all the new users with first activities after 7/1/2014 (note: this is updated on 12/5/15 when the competition restarted). In the sessions dataset, the data only dates back to 1/1/2014, while the users dataset dates back to 2010. 

https://www.kaggle.com/c/airbnb-recruiting-new-user-bookings/data

## Load Libraries and Data
```{r library}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(ggridges))
suppressPackageStartupMessages(library(lubridate))
suppressPackageStartupMessages(library(mice))
suppressPackageStartupMessages(library(caret))
```


```{r Load Data, message=FALSE, warning=FALSE}
data_path <- paste0(here::here(), '/Data/')
users_train <- read.csv(paste0(data_path,"train_users_2.csv"), na = c("", "-unknown-"))
age_gender_bkts <- read.csv(paste0(data_path,"age_gender_bkts.csv"))   
sessions <- read.csv(paste0(data_path,"sessions.csv"))
countries <- read.csv(paste0(data_path,"countries.csv"))

# Load helper functions
source("helper_function.R")
```


## Clean session


#### Action Group
```{r Missing Value Handling, message=FALSE}
#' Only keep the session data relavant to test & train set, key = user_id
sessions <- sessions %>% filter(user_id %in% users_train$id)

#' Deal with Missing Values
#' Fill na is time elpse with 0 
#' Change -unknown- level in action, action_type, action_detail to NA
#' Drop rows for which "user_id == NA"
sessions <- sessions %>% mutate(secs_elapsed = replace_na(secs_elapsed, 0)) %>% drop_na(user_id)

```


```{r Action Group Frequency Encoding}
# Compute the number unique actions (action_group) each user performed
num_diff_actions <- sessions %>% 
  mutate(action_group = paste(action, action_type, action_detail, sep = "/")) %>%
  select(user_id, action_group) %>% 
  group_by(user_id) %>% summarise(num_diff_action = n_distinct(action_group))

# Compute the number different of actions each user performed in total
actions <- sessions %>% 
  group_by(user_id) %>% summarise(total_action = n()) %>% 
  left_join(num_diff_actions)
rm(num_diff_actions)

#' Plot distribution of total action, it is found that the original data is heavily left skewed
#' A log transformation is then applied as a solution
actions %>% ggplot(aes(x = total_action)) + geom_histogram()
actions %>% ggplot(aes(x = log(total_action))) + geom_histogram()

actions %>% ggplot(aes(x = num_diff_action)) + geom_histogram()
actions %>% ggplot(aes(x = log(num_diff_action))) + geom_histogram()

# Apply log transformation
actions <- actions %>% mutate(log_total_action = log(total_action),
                              log_unique_actionTrp = log(num_diff_action),
                              total_action = NULL, num_diff_action = NULL)

```


#### Device
```{r}
# Category count check
# sessions %>% ggplot(aes(device_type)) +geom_bar()

# Combine device type categories into four main ones: Windows, Android, Apple
orgn_cate <- sessions$device_type %>% factor() %>% levels()
new_cate <- c("Other", rep("Android", 3), "Windows", rep("Apple",3), "Other", "Apple", "Android",
              "Android", rep("Windows", 2))
devices <- sessions %>% mutate(devices = plyr::mapvalues(device_type, from = orgn_cate, to = new_cate), 
                               device_type = NULL) %>%
  group_by(user_id, devices) %>% summarise(total_secs = sum(secs_elapsed), .groups = "keep") %>% 
  ungroup() %>% 
  pivot_wider(names_from = devices, values_from = total_secs, id_cols = user_id, values_fill = 0)
```


```{r message=FALSE}
# Plot Category to obtain transformation details

devices %>% ggplot(aes(x = Apple)) + geom_histogram()
devices %>%  ggplot(aes(x = (Apple^(1/3)))) + geom_histogram() # Too many 0s --> binning

devices %>% ggplot(aes(x = Android)) + geom_histogram()
devices %>% ggplot(aes(x = (Android^(1/3)))) + geom_histogram() # Too many 0s --> binning

devices %>% ggplot(aes(x = Windows)) + geom_histogram()
devices %>% ggplot(aes(x = (Windows^(1/3)))) + geom_histogram() # Too many 0s --> binning

devices %>% ggplot(aes(x = Other)) + geom_histogram()
devices %>% ggplot(aes(x = log(Other))) + geom_histogram() # bimodal distribution -> binning

```

```{r}
# Device transformation
device_trans <- devices %>% mutate(cbrt_Apple = Apple^ (1/3), cbrt_Android = Android^(1/3),
                                   cbrt_Windows = Windows^(1/3)) %>% 
  select(-c(Apple, Android, Windows))

# Log breaks and bin
otherBreaks <- c(-1, exp(8.5), max(devices$Other))
device_trans <- device_trans %>% mutate(OtherCate = cut(Other, otherBreaks)) %>% select(-Other)

# cbrt Breaks
cbrt_AppleBreaks <- c(-0.01, 0.01,
                      quantile(device_trans$cbrt_Apple[device_trans$cbrt_Apple != 0 ], 0.5),
                      max(device_trans$cbrt_Apple))
cbrt_AndroidBreaks <- c(-0.01, 0.01,
                        quantile(device_trans$cbrt_Android[device_trans$cbrt_Android != 0 ], 0.5),
                        max(device_trans$cbrt_Android))
cbrt_WindowsBreaks <- c(-0.01, 0.01,
                        quantile(device_trans$cbrt_Windows[device_trans$cbrt_Windows != 0 ], 0.5),
                        max(device_trans$cbrt_Windows))
# cbrt Binned
device_trans <- device_trans %>% mutate(AppleCate = cut(cbrt_Apple, cbrt_AppleBreaks),
                                        AndroidCate = cut(cbrt_Android, cbrt_AndroidBreaks),
                                        WindowsCate = cut(cbrt_Windows, cbrt_WindowsBreaks)) %>% 
  select(-c(cbrt_Apple, cbrt_Android, cbrt_Windows))

```



```{r}
# Plot distribution after binning
airbnb_train %>% ggplot(aes(x = AppleCate)) + geom_histogram(stat = "count")
airbnb_train %>% ggplot(aes(x = AndroidCate)) + geom_histogram(stat = "count")
airbnb_train %>% ggplot(aes(x = WindowsCate)) + geom_histogram(stat = "count")
airbnb_train %>% ggplot(aes(x = OtherCate)) + geom_histogram(stat = "count")
```

### Join Action & Device

```{r}
new_session <- full_join(actions, device_trans, by = "user_id")
```


## Joining with user_train
```{r}
airbnb_train <- inner_join(users_train, new_session, by = c("id" = "user_id"))
```


## User Data Transformation

### Missing Value Handling

Varaibles in `airbnb_train`: 
- id: user id  
- date_account_created: the date of account creation  
- timestamp_first_active: timestamp of the first activity, note that it can be earlier than  
(date_account_created or date_first_booking because a user can search before signing up)
- date_first_booking: date of first booking  
- gender  
- age  
- signup_method  
- signup_flow: the page a user came to signup up from  
- language: international language preference  
- affiliate_channel: what kind of paid marketing  
- affiliate_provider: where the marketing is e.g. google, craigslist, other  
- first_affiliate_tracked: whats the first marketing the user interacted with before the signing up  
- signup_app  
- first_device_type  
- first_browser  
- country_destination: response var  

```{r}
######################################################## Age 32412 missing value (43.9%) 

# Age abnormal case 1: the data is collected in 2015, according to the Airbnb term of use, the minimum age required for account creation is 18, so I assume ages < 18 are faulty inputs

# Age abnormal case 2: similarily, for those who wrong entered year as age, if it's greater than 2015-18 = 1997, it's faulty entry

# convert these problematic age entries as NA
airbnb_train$age[airbnb_train$age < 18 | airbnb_train$age > 1997] <- NA

# convert problematic year entry to age
airbnb_train <- airbnb_train %>% 
  mutate(true_age = ifelse(age > 1000, 2015 - age, age))
  
######################################################## Gender (37788 missing value) - (51.2%)
nrow(airbnb_train %>% 
  filter(is.na(gender))) 


# since it's far beyond acceptable proportion of missing value in terms of age and gender, I think a complete case analysis is perhaps more reasonable than imputed data analysis 
airbnb_train_cc <- airbnb_train %>% 
  filter(!is.na(gender) & !is.na(age))
```

```{r visualize missingness in gender and age, fig.width=8, fig.height=3}
destination_prop_plot(airbnb_train_cc)
destination_prop_plot(airbnb_train)
```



```{r check data missing for other char columns}
map(airbnb_train, ~sum(is.na(.))/nrow(airbnb_train))
map(airbnb_train_cc, ~sum(is.na(.))/nrow(airbnb_train_cc))


# date_first_booking: 16565; 48.1%
# drop this column 

# first_affiliate_tracked: 126 (0.3%)
# treat missing value as a separate category 


# first_browser: 5204 (15.1%)
# treat missing value as a separate category 
```


```{r convert data col & convert char to factor, warning = FALSE}
airbnb_cc <- airbnb_train_cc %>%
  mutate(
    date_first_active = as.Date(ymd_hms(timestamp_first_active),'%Y-%m-%d'),
    date_account_created = as.Date(date_account_created, '%Y-%m-%d'),
    date_first_booking = as.Date(date_first_booking, '%Y-%m-%d')
  ) %>% 
  relocate(date_first_active, .before = date_first_booking) %>%
  select(-timestamp_first_active) 
```


```{r check the factor cols (contingency table)}
# contingency table of each factor column
# print(category_count(airbnb_cc))

# combine categories with small counts 
airbnb_cleaned <- category_comb(airbnb_cc)

# contingency table of each factor column
# print(category_count(airbnb_cleaned))

# further merge categories
airbnb_cleaned <- category_comb_II(airbnb_cleaned)


# re-factor the categories 
airbnb_cleaned <- airbnb_cleaned %>% 
  mutate_if(is.character, factor) %>% 
  mutate_if(is.factor, factor)

# sort the destinations
airbnb_cleaned <- des_sorter(airbnb_cleaned)
  
# check the count of each category in each categorical variable again 
category_count(airbnb_cleaned)
```


### True Age filtering
```{r}
# Filter out unreasonable age
airbnb_cleaned <- airbnb_cleaned %>% filter(true_age < 95) %>% 
  mutate(log_age = log(true_age)) %>% 
  select(-c(id, date_first_booking, age, true_age))

#' Date encoding
#' Since the Data set is taken from 2015, we decide to change data information to the number of days
#' away from 2015/01/01
target_date <- as_datetime("2015/01/01")
airbnb_cleaned <- airbnb_cleaned %>% mutate(
  date_account_created = target_date - as_datetime(date_account_created),
  date_first_active = target_date - as_datetime(date_first_active))

# Check for transformation in date variables
airbnb_cleaned %>% ggplot(aes(x = date_account_created)) + geom_histogram()
airbnb_cleaned %>% ggplot(aes(x = date_first_active)) + geom_histogram()
```

### Data Split For Five Fold cross validation
```{r}
load(paste0(here::here(), "/Data/airbnb.RData"))

set.seed(2023)
folds <- createFolds((airbnb_cleaned %>% lapply(as.factor))$country_destination, k = 5)
```


### Save Data
```{r}
# save(airbnb_cleaned, folds, file = paste0(here::here(),"/Data/","airbnb.RData"))
```


