---
title: "Multinomial Logistic Regression"  
author: Shuyi Tan  
output: github_notebook  
editor_options: 
  chunk_output_type: inline
---

This file fits and tests four multinomial logitstic regression model:  
- Full model  
- Subset model based on stepwiseAIC  
- Oversampled full model  
- Undersampled  full model 

Models are evaluated by the following metric based on five-fold cross validation:    
- `mis_res_pred_int`: misclassification rate of 50% and 80% prediction interval  
- `mis_res_point_pred`: misclassification rate of point prediction   
- `IS`: interval score  
- `AUC`:  AUC value 


```{r}
suppressPackageStartupMessages(library(nnet))
suppressPackageStartupMessages(library(caret))
suppressPackageStartupMessages(library(tidyverse))

```

```{r Source the wrapper functions}
source(paste0(here::here(), '/Code/helper_function.R'))
source(paste0(here::here(), '/Code/modeling_function.R'))
```

```{r}
load(paste0(here::here(), "/Data/airbnb_cleaned.Rdata"))

# Rename the dataset to avoid misunderstanding 
airbnb_data <- airbnb_cleaned

# move the response variable to the last position for convenience
airbnb_data <-
  airbnb_data %>% relocate(country_destination, .after = 'log_age')
```




## Full model 

```{r}
full_multinom_logit <- multinom_logit_fitting(airbnb_data)
full_multinom_logit
```

## Subset Model with StepwiseAIC 

```{r}
sub_multinom_logit <- multinom_logit_fitting(airbnb_data, stepwise = TRUE)
sub_multinom_logit
```

## Oversampling
```{r}
multinom_logit_oversample <- multinom_logit_resampling(airbnb_data, 'over')
multinom_logit_oversample
```

## Undersampling

```{r}
multinom_logit_oversample <- multinom_logit_resampling(airbnb_data, 'under')
multinom_logit_oversample
```

