---
title: "Modeling - Naive Bayes"
output: github_document  
author: Shuyi Tan
editor_options: 
  chunk_output_type: inline
---

This notebook contains the modeling process of naive Bayes. Starting from a full model, we then moved to fit a subset model after removing highly correlated variables. Besides, we also trying two models with the oversampled and undersampled data respetively using a subset of variables from the second model.   

Each model is evaluated with five-fold misclassification rates based on 50% and 80% prediction interval. 

```{r Set up Package}
suppressPackageStartupMessages(library(tidyverse))
suppressForeignCheck(library(e1071))
suppressPackageStartupMessages(library(caret))
suppressPackageStartupMessages(library(GoodmanKruskal))
suppressPackageStartupMessages(library(pROC))
```


```{r Source the wrapper functions}
source(paste0(here::here(), '/Code/helper_function.R'))
source(paste0(here::here(), '/Code/modeling_function.R'))
```


```{r Load Data}
# Load the dataset
load("~/Desktop/Academic/STAT447/Airbnb-New-User-Bookings/Data/airbnb_cleaned.Rdata")

# Rename the dataset to avoid misunderstanding 
airbnb_data <- airbnb_cleaned

# move the response variable to the last position for convenience
airbnb_data <-
  airbnb_data %>% relocate(country_destination, .after = 'log_age')
```



# Naive Bayes Model 

## Fit full model 
```{r Full Model}
res_full <- NB_fitting(airbnb_data)
res_full
```


## Remove four variables with high correlation 
By some literature searching, we found that there are two sets of variables that may be highly correlated. The first set is   
* signup_app  
* signup_flow  
* signup_method  


the second set is  
* first_affiliate_tracked  
* affiliate_channel  
* affiliate_provider  

the third set is  
* first_browser  
* first_device_type  

We check the association between categircal variables with the Goodman-kruskal tau. 

```{r CorrPlot of all categorical predictors}
# filter all categircal predictors 
airbnb_data_cat<- airbnb_data %>%
  select(c(3:11))

# check the correlation with with the Goodman-kruskal tau
GKmat <- GKtauDataframe(airbnb_data_cat)
plot(GKmat, diagSize = 0.8)
```

```{r CorrPlot of a subset of  categorical predictors}
# remove highly correlated predictors 
airbnb_data_sub <- airbnb_data %>% 
  select(-c(signup_app, signup_flow, affiliate_channel, affiliate_provider, first_device_type))

# re-calculate the Goodman-kruskal tau
airbnb_data_sub_cat <- 
  airbnb_data_sub %>% select(c(3:7))
GKmat_sub <- GKtauDataframe(airbnb_data_sub_cat)
plot(GKmat_sub, diagSize = 0.8)
```


Therefore we will drop the following variables for the substted model:    
* signup_app  
* signup_flow  
* affiliate_channel  
* affiliate_provider  
* first_device_type   


and re-fit the Naive Bayes classifier. The results are as shown below:  

```{r Fit Model on a subset of predictors}
res_sub <- NB_fitting(airbnb_data_sub)
res_sub
```

## Further tackled imbalanced classification 
Either in each fold or the whole dataset, the proportion of categories in the response vairable is: 
* `other`: 15%  (minority)
* `US`: 37%  
* `NDF`:  48%  

```{r}
# check the imbalance in the repsonse variable
# the whole dataset
destination_prop_tb(airbnb_data_sub)
# each fold
for (i in 1:5) {
  fold = extract_folds(airbnb_data_sub, i, folds)
  print(destination_prop_tb(fold))
}
```

### Oversampling
```{r Fit a NB model with over sampling}
res_sub_oversample <- NB_fitting_resampling(airbnb_data_sub, 'over')
res_sub_oversample
```
### Undersampling 
```{r Fit a NB model with under sampling}
res_sub_undersample <- NB_fitting_resampling(airbnb_data_sub, 'under')
res_sub_undersample
```









